---
title: "Getting Started with hexmakR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with hexmakR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 3,
  fig.height = 3.46,  # 3 / (sqrt(3)/2) for correct hex ratio
  eval = FALSE
)
```

```{r logo, echo=FALSE, eval=TRUE, out.extra='style="float:right; margin-left:1em;"'}
logo <- system.file("logo", "logo.svg", package = "hexmakR")
if (nzchar(logo)) knitr::include_graphics(logo)
```

## Installation

Install hexmakR from CRAN:

```{r install-cran}
install.packages("hexmakR")
```

Or install the development version from GitHub:

```{r install-github}
# install.packages("pak")
pak::pak("r-heller/hexmakR")
```

## Your first hex sticker in 3 lines

```{r first-sticker}
library(hexmakR)

hex_sticker("mypackage", icon = "atom", theme = "stats")
```

That's it. The default settings produce a dark-themed sticker with the
`stats` color palette and an atom icon.

## Saving to a file

Pass `filename` to write a transparent PNG directly:

```{r save-sticker}
hex_sticker(
  "mypackage",
  icon     = "dna",
  theme    = "genomics",
  filename = "man/figures/logo.png"
)
```

The file will have the correct hexb.in aspect ratio (width / height = √3 / 2)
and a transparent background, ready for use in your README or pkgdown site.

## Exploring themes

```{r list-themes}
names(hexmakr_themes())
```

Preview a theme interactively:

```{r preview-theme}
hexmakr_preview_theme("genomics", mode = "dark")
hexmakr_preview_theme("genomics", mode = "light")
```

## Exploring icons

```{r list-icons}
# All categories
names(hexmakr_icons())

# Icons in a specific category
hexmakr_icons("biology")
```

## Customizing colors

Override any theme color individually:

```{r custom-colors}
hex_sticker(
  "mypackage",
  theme        = "stats",
  mode         = "dark",
  bg           = "#0D1117",
  accent       = "#58A6FF",
  text_color   = "#FFFFFF",
  border_color = "#58A6FF",
  sub_color    = "#8B949E"
)
```

## Choosing a font

```{r font}
hex_sticker(
  "mypackage",
  font_family = "serif",
  font_bold   = TRUE,
  font_italic = TRUE,
  font_size   = 14
)
```

Available font shorthands: `"mono"`, `"courier"`, `"consolas"`,
`"source_code"`, `"fira_code"`, `"serif"`, `"times"`, `"palatino"`,
`"sans"`, `"helvetica"`, `"roboto"`, `"open_sans"`, `"lato"`.

## Next steps

- For full parameter reference: `vignette("programmatic-usage")`
- To use the interactive designer: `vignette("shiny-app")` or just run
  `hexmakr_app()`
